---
title: "Check GH size"
author: "Giselle Schmitz"
date: "6/15/2022"
output: github_document
vignette: >
  %\VignetteIndexEntry{Check GH size}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

This package checks github repo size as a means of avoiding errors or oversized repos. The package will flag repos over a standard size.

## Installation

Install package using the code below:

```{r setup_pkgs, eval= FALSE}

install.packages("remotes")
remotes::install_github("nmfs-ost/ghBackup")
library(ghBackup)
```

## Using the `dir_size` function

The function uses the identified path to check the size of a specified directory and will return the total size.

```{r message=FALSE, warning=FALSE, results=FALSE}
object = ghBackup::dir_size(path=system.file("extdata", package="ghBackup"))
```

## Output

This output will show a table including the total directory size in MB and the full path to directory to be sized.

```{r message=FALSE, warning=FALSE, results=TRUE}
knitr::kable(object)
```
